### 2016-06-03 tasks_and_ideas.tex
cheers
tasks

\item Break a Squid server!  I'm thinking about a privacy break here.  One could start by simulating the (very simple) Bloom filter that Squid implements, and eventually stand up an actual Squid proxy.  Perhaps populate the filter with a random sampling of URLs from the Alexa top 1000.  (How large a sample?)  Given access to the filter, we can probably use the same attacks leveraged by Niedermayer et al.\ to infer information about which URLs are cached.  Of course, there's a timing based attack, just pinging the Squid proxy with URLs.   But this is probably harder than it sounds, and I don't know if/how Squid updates its filter on false-positive/cache misses. \tsnote{Apparently Crosby and Wallach gives some attacks.} \tsnote{Gerbet et al. give some generic attacks that are interesting.  I wonder if Squid, because it uses MD5, admits faster ``pollution attacks'' on the filter, e.g. where the adversary finds URLs that would set far more bits to 1 than one would expect?}

@@

>>>>

\item Break a Squid server!  I'm thinking about a privacy break here.  One could start by simulating the (very simple) Bloom filter that Squid implements, and eventually stand up an actual Squid proxy.  Perhaps populate the filter with a random sampling of URLs from the Alexa top 1000.  (How large a sample?)  Given access to the filter, we can probably use the same attacks leveraged by Niedermayer et al.\ to infer information about which URLs are cached.  Of course, there's a timing based attack, just pinging the Squid proxy with URLs.   But this is probably harder than it sounds, and I don't know if/how Squid updates its filter on false-positive/cache misses. \tsnote{Apparently Crosby and Wallach gives some attacks.} \tsnote{Gerbet et al. give some generic attacks that are interesting.  I wonder if Squid, because it uses MD5, admits faster ``pollution attacks'' on the filter, e.g. where the adversary finds URLs that would set far more bits to 1 than one would expect? (Yep, see Crosby and Wallach.)}

@@

\item What about breaking, via a real attack that we implement, things like HBase that use non-cryptographic hash functions?  (HBase apparently uses the Murmur hash.)  If there's a really damaging attack, and a plausible opportunity for someone to mount it, then that would be pretty slashy.
